The Controlled Choice Design and Paternalism in Pawnshop Borrowing

### 2023-10-16 donde.tex
cleaning of project folder - build replication files

Figure \ref{fan_park_bounds} plots the sharp bounds for $F_{\delta}$ based on the APR outcome defined above in Section \ref{costs}. Our point estimates of $\underline{F}(0)$ and $\overline{F}_0$ are .03 and .77 respectively, with associated 95\% confidence intervals of [0.024, 0.050] and [0.75, 0.80], which says that at least 23\% of individual borrowers benefit from commitment (and at most 97\%).\footnote{Confidence intervals are constructed using the asymptotic distribution for the bounds. See \cite{fan2010sharp} for details.}

@@

\vspace{.3in}
\begin{figure}[H]
    \caption{Fan \& Park bounds for benefit in APR\%}
    \label{fan_park_bounds}
    \begin{center}
    \begin{subfigure}{0.75\textwidth}
        \caption{APR}
        \centering
        \includegraphics[width=\textwidth]{Figuras/fan_park_bounds_apr.pdf}
    \end{subfigure}
    \end{center}
        \scriptsize
    This figure depicts the \cite{fan2010sharp} bounds on the distribution $F_\Delta$ of individual treatment effects $\Delta \equiv (Y_1 - Y_0)$, described in Section \ref{sec:bounds}, for the APR outcome.
    The dark red curve and light red shaded region give the estimated upper bound function $\overline{F}$ for $F_\Delta$ and associated (pointwise) 95\% confidence interval. 
    The dark blue curve and light blue shaded region give the estimated lower bound function $\underline{F}$ for $F_\Delta$ and associated (pointwise) 95\% confidence interval.
    Confidence intervals are computed using the asymptotic distribution for the bounds. See \cite{fan2010sharp} for details.
    The bounds are pointwise sharp: at any specified value of $\delta$ the bounds $\underline{F}(\delta) \leq F_\Delta(\delta) \leq \overline{F}(\delta)$ cannot be improved without imposing additional assumptions.
    Evaluating the bounds at $\delta = 0$, we see that between 24\% and 97\% of borrowers have a positive individual treatment effect.
    This is greater than the share of borrowers who chose commitment: 11\%.
%\textit{Do file: } \texttt{fan\_park\_bnds.do}       
\end{figure}

>>>>

Figure \ref{fan_park_bounds} plots the sharp bounds for $F_{\delta}$ based on the APR outcome defined above in Section \ref{costs}. Our point estimates of $\underline{F}(0)$ and $\overline{F}_0$ are .03 and .77 respectively, with associated 95\% confidence intervals of [0.025, 0.050] and [0.75, 0.80], which says that at least 23\% of individual borrowers benefit from commitment (and at most 97\%).\footnote{Confidence intervals are constructed using the asymptotic distribution for the bounds. See \cite{fan2010sharp} for details.}

@@

\vspace{.3in}
\begin{figure}[H]
    \caption{Fan \& Park bounds for benefit in APR\%}
    \label{fan_park_bounds}
    \begin{center}
    \begin{subfigure}{0.75\textwidth}
        \caption{APR}
        \centering
        \includegraphics[width=\textwidth]{Figuras/fan_park_bounds_apr.pdf}
    \end{subfigure}
    \end{center}
        \scriptsize
    This figure depicts the \cite{fan2010sharp} bounds on the distribution $F_\Delta$ of individual treatment effects $\Delta \equiv (Y_1 - Y_0)$, described in Section \ref{sec:bounds}, for the APR outcome.
    The dark red curve and light red shaded region give the estimated upper bound function $\overline{F}$ for $F_\Delta$ and associated (pointwise) 95\% confidence interval. 
    The dark blue curve and light blue shaded region give the estimated lower bound function $\underline{F}$ for $F_\Delta$ and associated (pointwise) 95\% confidence interval.
    Confidence intervals are computed using the asymptotic distribution for the bounds. See \cite{fan2010sharp} for details.
    The bounds are pointwise sharp: at any specified value of $\delta$ the bounds $\underline{F}(\delta) \leq F_\Delta(\delta) \leq \overline{F}(\delta)$ cannot be improved without imposing additional assumptions.
    Evaluating the bounds at $\delta = 0$, we see that between 23\% and 97\% of borrowers have a positive individual treatment effect.
    This is greater than the share of borrowers who chose commitment: 11\%.
%\textit{Do file: } \texttt{fan\_park\_bnds.do}       
\end{figure}

### 2023-10-16 presentation.tex
add row to hit-miss table for chocie rule & text editing
cleaning of project folder - build replication files

\begin{frame}{Context}
\begin{columns}
\begin{column}{.45\textwidth}
\begin{figure}[H]
    \begin{center}
    \caption{Pawnshop}
        \includegraphics[width=0.95\textwidth]{Figuras/empenio2.png}
    \end{center}
    \end{figure}
\begin{figure}[H]
    \begin{center}
    \caption{Appraisers  inside a pawnshop}
        \includegraphics[width=0.95\textwidth]{Figuras/empenio9.png}
    \end{center}
    \end{figure}    
    \end{column}
\begin{column}{.45\textwidth}
\begin{figure}[H]
    \begin{center}
    \caption{Waiting for appraisal}
        \includegraphics[width=0.95\textwidth]{Figuras/empenio11.png}
    \end{center}
    \end{figure}
\begin{figure}[H]
    \begin{center}
    \caption{Lost pawns which are for sale}
        \includegraphics[width=0.95\textwidth]{Figuras/empenio3.png}
    \end{center}
    \end{figure}    
    \end{column}    
    \end{columns}
\end{frame}

@@

\begin{frame}{Pawn contract}
    \begin{figure}[H]
    \label{ExplanatoryMaterial}
    \begin{center}
        \includegraphics[width=0.45\textwidth]{Figuras/sq_contract.png}
    \end{center}
\end{figure}
\end{frame}

\begin{frame}{Structured payments contract}
   \begin{itemize}
       \vfill \item We designed a new contract that is identical to the status quo contract except that it enhances the regularity and salience of payments as a way to encourage repayment.
         \begin{figure}[H]
    \label{ExplanatoryMaterial}
    \begin{center}
        \includegraphics[width=0.40\textwidth]{Figuras/fc_contract.png}
    \end{center}
\end{figure}

@@

   \begin{equation*}
    \text{Financial Cost}_i =  \underbrace{\sum_t P^i_{it}}_{\text{Pay to Interest}} + \underbrace{\sum_t P^f_{it}}_{\text{Pay to Fees}}  + \mathds{1}(\text{Default}_i) \times \left[\text{Pawn Val}_i + \underbrace{\sum_t P^c_{it}}_{\text{Pay to Capital}} \right]
   \end{equation*}

@@

\begin{itemize}
    \item Financial cost reduced by \$379 pesos (20\% of mean). That is: charging fee + structure \textit{decreased} cost.
    \item Default decreases by 6.5pp (15\% of mean).
    \item APR decreases by 34 points, from mean of 184.
\end{itemize}
\vspace{.3in}
\begin{table}[H]
\begin{center}
\resizebox{0.95\textwidth}{!}{
\small{\input{./Tables/decomposition_main_te_pres1.tex}}
}
\end{center}
\end{table}

@@

\begin{table}[H]
\caption{Intermediate outcomes}
\begin{center}
\scriptsize{\input{./Tables/mechanism1_pres.tex}}
\end{center}
\end{table}
\vfill
%\hyperlink{intermediate_outcomes}{\beamerbutton{Back}}
 \begin{itemize}
     \item \textbf{Speed of payment:} The first payment of the forced commitment contract  occurs 13 days earlier, increasing the fraction who recover on the first visit by 7.9 pp. Conditional on recovering, they recover 28 days faster.
\end{itemize}
\end{frame}

@@

\begin{table}[H]
\caption{Intermediate outcomes}
\begin{center}
\footnotesize{\input{./Tables/mechanism2_pres.tex}}
\end{center}
\end{table}

@@

    \begin{table}[H]
\caption{Intermediate outcomes}
\begin{center}
\footnotesize{\input{./Tables/mechanism3_pres.tex}}
\end{center}
\end{table}
\vfill
%\hyperlink{intermediate_outcomes}{\beamerbutton{Back}}
 \begin{itemize}
     \item \vfill \textbf{Frequency of visits:} Commitment induces a `parting of the waters' whereby those who were going to default visit the branch subsequently .2 fewer times.
\end{itemize}
\end{frame}

@@

\begin{frame}{Costs fall from Forcing by multiple measures}
\label{several_def_cost}
\begin{table}[H]
\caption{Effects on several definitions of cost}
\label{table_robustness_fc}
\begin{center}
\resizebox{0.95\textwidth}{!}{
\small{\input{./Tables/fc_robustness_pres.tex}}
}
\end{center}
 \scriptsize

@@

\begin{frame}{On avg. those that do not choose would benefit: TuT $>$ 0}
\begin{itemize}
    \vfill \item Commitment increases average financial benefit even for the subset of borrowers who \alert{don't choose to commit voluntarily}.
    \vfill \item Coefficient ToT>TuT, but cannot reject equality due to large s.e. in ToT.
    \vfill \item Results hold when imputing transport cost and lost wages per visit, and charge interest in amount paid (as a proxy for liquidity lost).
\end{itemize}
\vspace{.2in}
\begin{table}[H]
%those who are most likely to benefit from it and those whose outcomes are most adverse under the status quo.
\label{tot_tut}
\begin{center}
\small{\input{./Tables/tot_tut_pres1.tex}}
\end{center}
\end{table}
\end{frame}

@@

    \textbf{Do people learn from Forced exposure to the program that they benefit from it? } 
    \vspace{.1in}
    \begin{itemize}
    \item  Small sample (small power): focus on those that, after being either forced to commitment contract or to status quo, come back within a few months and are subject to choice arm.
    \vspace{.1in}
    \item  \textbf{No learning?} We don't find that being forced to the commitment contract makes them more likely to voluntarily chose commitment later.
    %\vfill \item Are people learning? \hyperlink{learning_table}{\beamerbutton{Table}}
 \end{itemize}  
 \vspace{.2in}
\begin{table}[H]
\begin{center}
\small{\input{./Tables/learning_exp_pres.tex}}
\end{center}
\end{table}
 %\hyperlink{learning}{\beamerbutton{Back}}
}

@@

    \begin{itemize}
    \item   We estimate the TuT conditional on $X_i=1$ or $X_i=1$ (say $X_i= PB_i$ or $=Confidence_i$) and see which subppulations have larger TuT.

@@

\begin{itemize}
    \item The TuT effect is concentrated on those that say they have 100\% of recovery. This is what we would expect if the Sure-confident don't demand because they think they don't need it (but are wrong).
    \item Also on those with no PB (as measured by us).
\end{itemize}
\begin{columns}
\begin{column}{.45\textwidth}
    \begin{figure}[H]
    \caption{TuT}
        \includegraphics[width=1.1\textwidth]{Figuras/tut_beh_partition.pdf}
\end{figure}
\end{column}

\begin{column}{.45\textwidth}
    \begin{figure}[H]
    \caption{ToT}
        \includegraphics[width=1.1\textwidth]{Figuras/tot_beh_partition.pdf}
\end{figure}
\end{column}
\end{columns}
\end{frame}

@@

    \begin{figure}
        \caption{CATE (APR)}
        \centering
        \includegraphics[width=0.5\textwidth]{Figuras/he_dist_apr_pro_2.pdf}
        \end{figure}

@@

    \begin{figure}
        \caption{Causal Tree}
        \centering
\includegraphics[width=0.8\textwidth]{Figuras/ct_eff.pdf}
        \end{figure}

@@

        \begin{figure}
        \label{choose_wrong}
        \caption{Mistakes in choice arm}
        \centering
        \includegraphics[width=0.65\textwidth]{Figuras/line_cw_apr_tot_tut.pdf}
        \end{figure}

@@

        \begin{figure}
         \label{better_forceall}
        \caption{Effect of forcing everyone}
        \centering
        \includegraphics[width=0.65\textwidth]{Figuras/line_better_forceall_apr_te_cf.pdf}
        \end{figure}

@@

\begin{frame}{Appraiser FE}
\label{clerk_fe}
\begin{table}[H]
\begin{center}
\resizebox{0.95\textwidth}{!}{
\small{\input{./Tables/clerk_fe.tex}}
}
\end{center}
 \scriptsize

%\textit{Do file: } \texttt{clerk\_fe.do}
\end{table}
    \hyperlink{main_results}{\beamerbutton{Back}}

@@

\begin{frame}{Censoring}
\label{censoring}
    \begin{table}[H]
\caption{Bounding censoring}
\label{bounding_censoring}
\begin{center}
\resizebox{0.9\textwidth}{!}{
\footnotesize{\input{./Tables/censoring_imp_pres.tex}}
}
\end{center}
 \scriptsize 
%\textit{Do file: } \texttt{censoring_imp.do, censoring_imp_pr.do}
\end{table}

@@

\begin{frame}{Bounding Individual Treatment Effects}
\label{fan_park_bounds}

\begin{figure}[H]
    \caption{Fan \& Park bounds for benefit in effective FC }

    \begin{center}
        \includegraphics[width=0.75\textwidth]{Figuras/fan_park_bounds_fc_admin.pdf}
    \end{center}

\end{figure}
 \hyperlink{choice_hte}{\beamerbutton{Back}}
\end{frame}

>>>>

\begin{frame}{Context}
\begin{columns}
\begin{column}{.45\textwidth}
\begin{figure}[H]
    \begin{center}
    \caption{Pawnshop}
        \includegraphics[width=0.95\textwidth]{Figuras/empenio2_.png}
    \end{center}
    \end{figure}
\begin{figure}[H]
    \begin{center}
    \caption{Appraisers  inside a pawnshop}
        \includegraphics[width=0.95\textwidth]{Figuras/empenio9_.png}
    \end{center}
    \end{figure}    
    \end{column}
\begin{column}{.45\textwidth}
\begin{figure}[H]
    \begin{center}
    \caption{Waiting for appraisal}
        \includegraphics[width=0.95\textwidth]{Figuras/empenio11_.png}
    \end{center}
    \end{figure}
\begin{figure}[H]
    \begin{center}
    \caption{Lost pawns which are for sale}
        \includegraphics[width=0.95\textwidth]{Figuras/empenio3_.png}
    \end{center}
    \end{figure}    
    \end{column}    
    \end{columns}
\end{frame}

@@

\begin{frame}{Pawn contract}
    \begin{figure}[H]
    \label{ExplanatoryMaterial1}
    \begin{center}
        \includegraphics[width=0.45\textwidth]{Figuras/sq_contract.png}
    \end{center}
\end{figure}
\end{frame}

\begin{frame}{Structured payments contract}
   \begin{itemize}
       \vfill \item We designed a new contract that is identical to the status quo contract except that it enhances the regularity and salience of payments as a way to encourage repayment.
         \begin{figure}[H]
    \label{ExplanatoryMaterial2}
    \begin{center}
        \includegraphics[width=0.40\textwidth]{Figuras/fc_contract.png}
    \end{center}
\end{figure}

@@

   \begin{equation*}
    \text{Financial Cost}_i =  \underbrace{\sum_t P^i_{it}}_{\text{Pay to Interest}} + \underbrace{\sum_t P^f_{it}}_{\text{Pay to Fees}}  + \mathds{1}(\text{Default}_i) \times \left[\text{(Appr. value - Loan Diff)}_i + \underbrace{\sum_t P^c_{it}}_{\text{Pay to Capital}} \right]
   \end{equation*}

@@

\begin{itemize}
    \item Financial cost reduced by \$379 pesos (20\% of mean). That is: charging fee + structure \textit{decreased} cost.
    \item Default decreases by 6.5pp (15\% of mean).
    \item APR decreases by 34 points, from mean of 184.
\end{itemize}
\vspace{.3in}
\begin{table}[H]
\begin{center}
\resizebox{0.95\textwidth}{!}{
\small{\input{./Tables/decomposition_main_te.tex}}
}
\end{center}
\end{table}

@@

\begin{table}[H]
\caption{Intermediate outcomes}
\begin{center}
\scriptsize{\input{./Tables/mechanism_pres1.tex}}
\end{center}
\end{table}
\vfill
%\hyperlink{intermediate_outcomes}{\beamerbutton{Back}}
 \begin{itemize}
     \item \textbf{Speed of payment:} The first payment of the forced commitment contract  occurs 13 days earlier, increasing the fraction who recover on the first visit by 7.9 pp. Conditional on recovering, they recover 28 days faster.
\end{itemize}
\end{frame}

@@

\begin{table}[H]
\caption{Intermediate outcomes}
\begin{center}
\footnotesize{\input{./Tables/mechanism_pres2.tex}}
\end{center}
\end{table}

@@

    \begin{table}[H]
\caption{Intermediate outcomes}
\begin{center}
\footnotesize{\input{./Tables/mechanism_pres3.tex}}
\end{center}
\end{table}
\vfill
%\hyperlink{intermediate_outcomes}{\beamerbutton{Back}}
 \begin{itemize}
     \item \vfill \textbf{Frequency of visits:} Commitment induces a `parting of the waters' whereby those who were going to default visit the branch subsequently .2 fewer times.
\end{itemize}
\end{frame}

@@

\begin{frame}{Costs fall from Forcing by multiple measures}
\label{several_def_cost}
\begin{table}[H]
\caption{Effects on several definitions of cost}
\label{table_robustness_fc}
\begin{center}
\resizebox{0.95\textwidth}{!}{
\small{\input{./Tables/fc_robustness.tex}}
}
\end{center}
 \scriptsize

@@

\begin{frame}{On avg. those that do not choose would benefit: TuT $>$ 0}
\begin{itemize}
    \vfill \item Commitment increases average financial benefit even for the subset of borrowers who \alert{don't choose to commit voluntarily}.
    \vfill \item Coefficient ToT>TuT, but cannot reject equality due to large s.e. in ToT.
    \vfill \item Results hold when imputing transport cost and lost wages per visit, and charge interest in amount paid (as a proxy for liquidity lost).
\end{itemize}
\vspace{.2in}
\begin{table}[H]
%those who are most likely to benefit from it and those whose outcomes are most adverse under the status quo.
\label{tot_tut}
\begin{center}
\small{\input{./Tables/tot_tut.tex}}
\end{center}
\end{table}
\end{frame}

@@

    \textbf{Do people learn from Forced exposure to the program that they benefit from it? } 
    \vspace{.1in}
    \begin{itemize}
    \item  Small sample (small power): focus on those that, after being either forced to commitment contract or to status quo, come back within a few months and are subject to choice arm.
    \vspace{.1in}
    \item  \textbf{No learning?} We don't find that being forced to the commitment contract makes them more likely to voluntarily chose commitment later.
    %\vfill \item Are people learning? \hyperlink{learning_table}{\beamerbutton{Table}}
 \end{itemize}  
 \vspace{.2in}
\begin{table}[H]
\begin{center}
\small{\input{./Tables/learning_exp.tex}}
\end{center}
\end{table}
 %\hyperlink{learning}{\beamerbutton{Back}}
}

@@

    \begin{itemize}
    \item   We estimate the TuT conditional on $X_i=1$ or $X_i=1$ (say $X_i= PB_i$ or $=Confidence_i$) and see which sub-populations have larger TuT.

@@

\begin{itemize}
    \item The TuT effect is concentrated on those that say they have 100\% of recovery. This is what we would expect if the Sure-confident don't demand because they think they don't need it (but are wrong).
    \item Also on those with no PB (as measured by us).
\end{itemize}
\begin{figure}[H]
    \caption{TuT}
        \includegraphics[width=0.5\textwidth]{Figuras/tut_beh_partition.pdf}
\end{figure}
\end{frame}

@@

    \begin{figure}
        \caption{CATT (APR)}
        \centering
        \includegraphics[width=0.5\textwidth]{Figuras/he_dist_tau_hat_tut.pdf}
        \end{figure}

@@

    \begin{figure}
        \caption{Causal Tree}
        \centering
\includegraphics[width=0.8\textwidth]{Figuras/crf_apr.pdf}
        \end{figure}

@@

        \begin{figure}
       % \label{choose_wrong}
        \caption{Mistakes in choice arm}
        \centering
        \includegraphics[width=0.65\textwidth]{Figuras/line_cw_apr_tot_tut.pdf}
        \end{figure}

@@

        \begin{figure}
         \label{better_forceall}
        \caption{Effect of forcing everyone}
        \centering
        \includegraphics[width=0.65\textwidth]{Figuras/cdf_CATE.pdf}
        \end{figure}

@@

@@

\begin{frame}{Censoring}
\label{censoring}
    \begin{table}[H]
\caption{Bounding censoring}
\label{bounding_censoring}
\begin{center}
\resizebox{0.9\textwidth}{!}{
\footnotesize{\input{./Tables/censoring_imp.tex}}
}
\end{center}
 \scriptsize 
%\textit{Do file: } \texttt{censoring_imp.do, censoring_imp_pr.do}
\end{table}

@@
